Real-time Attention Assessment for Social Robots

### 2015-09-14 paper.tex
Minor change to abstract

Successfully sustaining face-to-face interaction between humans and robots
mandates fine perception of each other attentional focus. Along this line, we
present a novel technique to assess the visual focus of attention (VFOA) based
on accurate, real-time head pose estimation with monocular camera. The software
is fully open-source and can readily be adopted on a wide range of social
robots. We propose an in-depth evaluation of the technique, using manual video
annotations as ground truth, and show that our system reaches high level of
accuracy in a real-world face-to-face interaction scenario. We finally show how
to derive a metric of engagement from the monitoring of the VFOA, allowing the
robot to account and react to the user's changing engagement in real-time.

>>>>

Successfully sustaining face-to-face interaction between humans and robots
mandates fine perception of each other attentional focus. Along this line, we
present a novel technique to assess the visual focus of attention (VFOA) based
on accurate, real-time head pose estimation with monocular camera. The software
is fully open-source and can readily be adopted on a wide range of social
robots. We propose an in-depth evaluation of the technique, using manual video
annotations as ground truth, and show that our system reaches high level of
accuracy in a real-world face-to-face interaction scenario. We finally suggest how
to derive a metric of engagement from the monitoring of the VFOA, allowing the
robot to account and react to the user's changing engagement in real-time.
